
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
\secretlevel{绝密} \secretyear{2100}

\ctitle{清华大学学位论文~\LaTeX\ 模板使用示例文档}
% 根据自己的情况选，不用这样复杂
\makeatletter
\ifthu@bachelor

\else
\ifthu@doctor
  \cdegree{工学博士}
\else
  \ifthu@master
    \cdegree{工学硕士}
  \fi
\fi
\fi
\makeatother


\caffil{计算机科学与技术系}
\caffilshort{计算机} 
\csubject{计算机科学与技术}
\cauthor{薛瑞尼} 
\studentid{2005310432}
\classid{计研~2}
\groupmemebers{edyfox}
\csupervisor{郑纬民教授}
% 如果没有副指导老师或者联合指导老师，把下面两行相应的删除即可。
\cassosupervisor{陈文光副教授}
\ccosupervisor{某某某教授}
% 日期自动生成，如果你要自己写就改这个cdate
%\cdate{\CJKdigits{\the\year}年\CJKnumber{\the\month}月}

\etitle{An Introduction to \LaTeX{} Thesis Template of Tsinghua University} 
\edegree{Doctor of Science} 
\esubject{Computer Science and Technology} 
\eauthor{Xue Ruini} 
\esupervisor{Professor Zheng Weimin} 
\eassosupervisor{Chen Wenguang} 
% 这个日期也会自动生成，你要改么？
% \edate{December, 2005}

%定义中英文摘要和关键字
\cabstract{
    本文介绍清华大学论文~\LaTeX + CJK
    模板的使用方法。本模板基本符合学校的博士、硕士
  论文格式要求。本科论文关键字用逗号分子，硕士论文为关键字之间为~2 个汉字字符，博士论
  文关键词之间为分号，你说麻烦不麻烦。大家在用的时候多多注意。具体使用方法请参看本文源文件。}

%根据你的情况，选择一个即可，这里只是作为示例。
\makeatletter
\ifthu@bachelor
  \ckeywords{\TeX，\LaTeX，CJK，模板，排版，论文}
\else
  \ifthu@master
    \ckeywords{\TeX\keyspace \LaTeX\keyspace CJK\keyspace 模板\keyspace 排版\keyspace 论文}
  \else
    \ckeywords{\TeX；\LaTeX；CJK；模板；排版；论文}
  \fi
\fi
\makeatother

 \eabstract{
  This article presents the \LaTeX + CJK template for Master Thesis of Tsinghua University, and briefly
  introduces the usage.

  The template has been verified by the Graduate School of Tsinghua
  University. It fulfils the corresponding format requirements. This document is
  generated according to the format of Master Thesis.  You possibly need to make
  some modification for Master Thesis.

  Generally, the abstract and the key words should be consistent with the
  Chinese version. The space between them is four english characters.  }

% 这里也是
\makeatletter
\ifthu@bachelor
   \ekeywords{\TeX，\LaTeX，CJK，template，typesetting，thesis}
\else
  \ifthu@master
    \ekeywords{\TeX\keyspace \LaTeX\keyspace CJK\keyspace template\keyspace  typesetting\keyspace thesis}
  \else
    \ekeywords{\TeX; \LaTeX; CJK; template;  typesetting; thesis}
  \fi
\fi
\makeatother


\contentsandprogress{这是主要进度}
\mainrequirements{这是主要要求（指标）}
\mainreferences{这是主要要求（指标）}